Title

### 2023-06-29 main.tex
No time to commit.. My people need me!

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
has to be constructed with only one parametrized rotation,
so it has to satisfy the conditions of theorem \ref{theorem2}.
}
\cpnote{Sigue estando redundante. Dices que cuales se pueden implentar con 1pr circuit y que 
enticones tiene que ser construidas con un 1pr. Quizá integra las dos frases o has algo}
Therefore, this implies that the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] 
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ a uniform random phase.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
unitaria. Aclarame ese punto y le sigo al resto del parrafo}
\tbnote{Ah, es que más bien la idea era primero decir que el siguiente paso es
usar una matriz unitaria (con la condición
mencionada sobre el primer renglón)
y explicar cómo la usamos y por qué.
Ya luego mostrar cómo se puede construir dicha 
matriz al azar. También se puede hacer al revés,
pero no me convencía decir todo lo de cómo 
construir la matriz sin decir antes para qué}
.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

@@

\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
del que croe que merece. Inspirate en la intro. }
\tbnote{Ah va, listo}

{\color{purple}
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities. 
Finally, when working with Pauli dynamical maps,
we searched for a way of simplifying the parametrized circuit
by requiring that only one single-qubit rotation depends on the parameter.
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.
}

@@

\nolinenumbers

@@

%\bibitem{bib3}
%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
%  infection through a transposon insertion followed by a {D}uplication}.
%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
%
%\end{thebibliography}
\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
\bibliography{Bibliography}

>>>>

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
For this, the curve of states of \eref{eq: parametrized state} 
has to be constructed with only one parametrized rotation,
so it has to satisfy the conditions of theorem \ref{theorem2}.
Therefore, this implies that the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] 
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ a uniform random phase.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
\eref{eq:conditions-vecs}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

@@

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities. 
Finally, when working with Pauli dynamical maps,
we searched for a way of simplifying the parametrized circuit
by requiring that only one single-qubit rotation depends on the parameter.
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.

Therefore, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.

@@

% \nolinenumbers

@@

%\bibitem{bib3}
%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
%  infection through a transposon insertion followed by a {D}uplication}.
%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
%
%\end{thebibliography}
\cpnote{Revisa con cuidado la bibliografia. Los nombres parece que estan bien, pero los doi parece que no estan completos. Hay nombres de revistas raros. Cre oque en plos one se abrevian, pero entonces haslos otodos abreviavos. Revis que todos tengan año, numero y pagina y que esté homogeneo. Revisa con cuidaod como son las abreviaciones de los journals (son estandard pero no recuerdo odnde está esa informacion). Ver revisando el procedimiento para someter a Plos One y al arxiv. Avisame cuando estes listo. }

\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
\bibliography{Bibliography}
